Perceptions of Corruption in Nigeria

### 2024-11-30 paper/paper.qmd
world bank refernce added

```{r}
#| label: fig-urban-rural-distribution
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Figure 1: Urban vs Rural Respondent Distribution. This bar chart compares the number of respondents residing in urban versus rural areas."

@@

```{r}
#| label: fig-corruption-presidency
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Figure 2: Perceived Corruption in the Presidency. This bar chart shows the distribution of respondents' perceptions of corruption in the presidency."

@@

```{r}
#| label: fig-age-group-distribution
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Figure 3: Age Group Distribution. This bar chart displays the number of respondents in each age group."

@@

```{r}
#| label: fig-trust-political-institutions
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Figure 4: Distribution of Trust in Political Institutions. This histogram shows how respondents rated their trust in political institutions, from low to high trust."

@@

```{r}
#| label: fig-demand-democracy
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Figure 5: Distribution of Demand for Democracy. This histogram illustrates respondents' levels of demand for democracy, with higher values reflecting stronger democratic preferences."

@@

## Variables of Interest

@@

## Corruption Perceptions Model
```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Summary of the Ordinal Logistic regression model"
#| warning: false

@@

```
@fig-predicted-probabilities illustrates the predicted probabilities derived from the Bayesian ordinal logistic regression model for different demographic predictors influencing corruption perceptions in Nigeria. Each bar represents the estimated impact of a specific predictor on the likelihood of perceiving higher corruption levels in the presidency.

>>>>

## Variables of Interest
```{r}
#| label: fig-urban-rural-distribution
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: " Urban vs Rural Respondent Distribution. This bar chart compares the number of respondents residing in urban versus rural areas."

@@

@fig-urban-rural-distribution illustrates the distribution of survey
respondents based on their residential location, categorized as urban or
rural. From this, we see that the sample has more rural residents
compared to urban residents. Specifically, the Afrobarometer survey for
Nigeria, conducted in 2022, reports that approximately 53% of Nigeria's
population resides in rural areas, this is is consistent with national
demographic trends [@worldbank2022rural]. This rural-urban distribution
is important for helping us understand the perspectives seen in the
survey, since rural populations may have different challenges in
governance and corruption compared to urban populations. The imbalance
in representation shows that looking at geographical disparities when
interpreting results from nationwide surveys is important.

```{r}
#| label: fig-corruption-presidency
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Perceived Corruption in the Presidency. This bar chart shows the distribution of respondents' perceptions of corruption in the presidency."

@@

@fig-corruption-presidency presents the distribution of respondents'
perceptions of corruption within the Nigerian presidency. The variable 
"Perceived Corruption in the Presidency" captures respondents' perceptions of 
the extent of corruption within the Nigerian presidency and its officials. This 
variable originates from Question 38A of the Afrobarometer survey, which asked:
*"How many of the following people do you think are involved in corruption, or 
haven’t you heard enough about them to say: the president and officials in his 
office?"* [@Afrobarometer2022codebook] Respondents could choose from the following values:

-   **0 (None)**: Indicates that the respondent perceives no corruption
    in the office of the presidency.
-   **1 (Some of them)**: Suggests that the respondent believes a few
    individuals in the presidency are involved in corruption.
-   **2 (Most of them)**: Reflects the perception that corruption is
    prevalent among the majority of the presidency's officials.
-   **3 (All of them)**: Suggests the respondent perceives widespread
    corruption, implicating all officials in the presidency.
-   **8 (Refused)**: Indicates the respondent declined to answer the
    question.
-   **9 (Don’t know/Haven’t heard enough)**: Suggests the respondent was
    unsure or lacked sufficient knowledge to provide an answer.
-   **-1 (Missing)**: Represents missing or unavailable responses.

For the analysis, only the substantive responses (0-3) were considered,
in order to help us look into perceptions of corruption within the presidency. 
The high frequency of responses in the "High Corruption" and "Some
Corruption" categories reflects persistent concerns about the integrity
of key officials in Nigeria, aligning with broader findings on
corruption in the region.@fig-corruption-presidency presents the distribution of 
respondents' perceptions of corruption within the Nigerian presidency. Among
these, the category "High corruption" is the most frequently reported,
followed by "Some corruption". "All corrupt" ranks third, with "No
Corruption" being the least chosen category which is no surprise given
our data is in the context of Nigeria. These proportions show
significant public concern about corruption within the presidency,
consistent with broader trends in public concern abut corruption
corruption within the presidency in Nigeria.

```{r}
#| label: fig-age-group-distribution
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Age Group Distribution. This bar chart displays the number of respondents in each age group."

@@

```
@fig-age-group-distribution illustrates the distribution of survey respondents across five distinct age groups: 18-24, 25-34, 35-44, 45-54, and 55+. The data reveals that the 25-34 age group is the most represented, with over 500 respondents, followed by the 35-44 age group. The youngest cohort, aged 18-24, comprises approximately 300 respondents, while the older age groups (45-54 and 55+) are less represented in the dataset, with fewer than 200 respondents each. This distribution highlights a concentration of responses from younger demographics, particularly those aged 25-34, which may reflect broader societal trends such as population age structure or survey reach and accessibility.
```{r}
#| label: fig-trust-political-institutions
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Distribution of Trust in Political Institutions. This histogram shows how respondents rated their trust in political institutions, from low to high trust."

@@

```{r}
#| label: fig-demand-democracy
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Distribution of Demand for Democracy. This histogram illustrates respondents' levels of demand for democracy, with higher values reflecting stronger democratic preferences."

@@

@@

## Corruption Perceptions Model

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Summary of the Ordinal Logistic regression model"
#| warning: false

@@

@fig-predicted-probabilities illustrates the predicted probabilities
derived from the Bayesian ordinal logistic regression model for
different demographic predictors influencing corruption perceptions in
Nigeria. Each bar represents the estimated impact of a specific
predictor on the likelihood of perceiving higher corruption levels in
the presidency.
